%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{\href{http://MichaelLuong.com}{\color{blue}Michael D Luong}} % Your name
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary address (optional)
\address{\href{mailto://Ask@MichaelLuong.com}{\color{blue}Ask@MichaelLuong.com} \\ Pittsburgh, PA} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

%----------------------------------------------------------------------------------------
%	Google
%----------------------------------------------------------------------------------------

\begin{rSubsection}{Google - GPay and Wallet SRE}{February 2022 - Present}{Software Engineer, Site Reliability Engineering}{Pittsburgh, PA}
\begin{itemize}
    \item \textbf{Critical User Interactions:} Using 
\end{itemize}
\begin{itemize}
    \item \textbf{PowerShell:} Owner of the Teams PowerShell module. Created and optimized commandlets for preview and GA module. C\#, PowerShell, Kusto
\end{itemize}
\end{rSubsection}

%----------------------------------------------------------------------------------------
%	Microsoft
%----------------------------------------------------------------------------------------

\begin{rSubsection}{Microsoft - Teams}{December 2019 - Present}{Software Development Engineer}{Bellevue, WA}
\begin{itemize}
    \item \textbf{Pre-GA:} Adds new security functionality automatically by restricting how information can be shared. Lead for the client team. React, Angular, GraphQL, Apollo
\end{itemize}
\begin{itemize}
    \item \textbf{PowerShell:} Owner of the Teams PowerShell module. Optimized commandlets for preview and GA module. C\#, PowerShell, Kusto
\end{itemize}
\end{rSubsection}

%----------------------------------------------------------------------------------------
%	Amazon
%----------------------------------------------------------------------------------------

\begin{rSubsection}{Amazon - Alexa}{July 2018 - October 2019}{Software Development Engineer II}{Seattle, WA}
\begin{itemize}
    \item \textbf{Alexa Contact Us:} Helped developers find self help articles and eliminated manual routing of contact cases. Lead engineer for externally facing site for developers to see self help material before submitting a contact. Designed APIs, data flow, data storage, front-end and back-end servers, dynamic page rendering, and dynamic team email mapping. JavaScript, Java, Spring MVC, DynamoDB
    \item \textbf{Unpublish service:} Eliminated the need for developers to submit a case if they wanted to hide or remove their skill. Reduced suppression related contacts by over 95\%. Java, PostgreSQL
\end{itemize}
\end{rSubsection}

%----------------------------------------------------------------------------------------
%	Liberty Mutual
%----------------------------------------------------------------------------------------

\begin{rSubsection}{Liberty Mutual Insurance - eService}{March 2018 - June 2018}{Software Developer / Machine Learning Engineer}{Boston, MA}
\begin{itemize}
    \item \textbf{Renewal:} Organized, filtered and combined data sources to answer business questions and created a likeliness of renewal model for next best action - Python, Scikit-learn, Adobe Analytics, Omniture, Opinion Labs, PostgreSQL
    \item \textbf{Service Website:} Created dozens of features using A/B tests to design a user friendly website. The user would spend less time on the website and not call. JS, React, Adobe Anaytics, Omniture
\end{itemize}
\end{rSubsection}

\begin{rSubsection}{Liberty Mutual Insurance - eSales}{Oct 2015 - March 2018}{Full Stack Developer}{Boston, MA}
\begin{itemize}
    \item \textbf{Strategic Revenue Generation:} Increased profit by designing an alternative revenue source by selling leads. Worked with third party vendors for contract negations, SLAs, and security reviews.
    \item \textbf{Next Best Action:} Created a model around the customer to provide a more personalized experience and to improve user satisfaction. The flow would change based on questions answered earlier.
    \item \textbf{POD:} Designed a modular framework in parallel to the main quoting application for more rapid hypothesis testing platform. It was used for testing and proving different technologies to see if they could be incorporated back into the main application - JS, ReactJS, WebSockets, NodeJS, Express
\end{itemize}
\end{rSubsection}

\begin{rSubsection}{Liberty Mutual Insurance - Surety}{Jan 2011 - Oct 2015}{Software Developer}{Plymouth Meeting, PA}
\begin{itemize}
    \item \textbf{Execute:} Lead developer of surety forms. In charge of front-end, back-end, networking, load balancing, CI/CD, database optimization. 
\end{itemize}
\end{rSubsection}
\end{rSection}


\begin{rSection}{Education}
\begin{rSubsection}{The Pennsylvania State University}{May 2010}{Bachelors - Computer Engineering}{University Park, PA}

\end{rSubsection}
\end{rSection}

\end{document}
